Discrete Quantum Theories and Computing

### 2018-12-21 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

After first suggested by Richard Feynman 40 years ago~\cite{Feynman1982Simulating},
IBM, \textitalian{Rigetti}, Google, Microsoft, and many other companies
and countries start to build realistic quantum computers recently
\cite{Shieber2018,Kahn2019}, and seek more efficient ways to simulate
chemical molecules and to break down RSA \cite{boneh1999twenty,wiki:RSAFactoring}.
No matter how to, classical or quantum, attack these two tasks, they
require two different types of quantities. On one hand, a question
and its answer of RSA are both discrete integers. On the other hand,
even if the quantities describing molecules, like the domain of their
position wave functions or the probability amplitudes of a wave function,
are considered as continuous, we want to argue that these quantities
might later be discovered as discrete. Even if they were not discrete,
this fact may never be proved and the exact value of these quantities
may never be pinned down. To better understand this issue without
struggling with the quantum theory, it is instructive to review how
classical quantities are characterized and computed.

@@

Although it is convenient to assume physical quantities is as continuous
as their mathematical models, each physical quantity discussed in
the previous paragraph could not have a simple one-to-one correspondence
with a real number. Chuang-tzu's stick are made by molecules and cannot
be cut in halves endlessly. The input charge of an integrator must
actually be an integer multiple of the elementary charge. A prefect
square cannot be draw physically. Even we don't draw it, but merely
ask whether it exists in the space. This question is still beyond
our ability to answer because whether the space itself is ultimately
discrete or continuous is still an unsolved question. Even if a prefect
square exists physically, we may not able to decide whether the “square”
we discussed is really prefect or almost prefect differing only by
an arbitrarily small extent. Similar situation applying to the length
of a slide rule, it is beyond our ability to decide whether its length
is ultimately discrete or continuous. Even if its length is continuous,
identifying which real number represents its length requires infinite
precision, but the precision in reality is limited generally three
or four significant figures~\cite{wiki:AnalogComputer}. As the results,
even if analog computers really store real numbers, they cannot be
precisely read, written, and used to branch the computation. The opposite
of the last statement is sometimes assumed by real computational models.
For example, Blum, Cucker, Shub, and Smale modeled their BCSS machine
to allow the operations of deciding whether a number is greater or
equal to zero over real numbers and whether a number is exactly zero
over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
Therefore, the computational power of analog computers is far weaker
than the prediction based on this kind of theoretical models.

\begin{sidewaystable}
\caption{\label{tab:Comparison}Comparison between the classical quantities
and their mathematical models with their inspired quantum models.
\todo{Center entries vertically.}}

\centering{}\centering{}%
\begin{tabularx}{\linewidth}{ccYY}
\toprule 
\addlinespace
Physical quantities & Discrete & Discrete with extreme small unit & Continuous?\tabularnewline\addlinespace
\addlinespace
\addlinespace
Computational devices & Digital computer & Analog computer & Analog computer\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Mathematical representation & Integers & Real numbers & Real numbers\tabularnewline\addlinespace
\addlinespace
\addlinespace
Computational model  & Turing machine & BCSS machine & BCSS machine\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
How the models realize? & Reliably & 
Not reliably, but after we have a better technology to manipulate the minimum units, we can predict the physical phenomenon and their computational power by a better discrete model. & 
Not reliably, because precision can never be high enough. \tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Inspired quantum models &  & Quantum Theories and Computing over Finite Fields & Quantum Interval-Valued Probability Measures (QIVPM)\tabularnewline\addlinespace
\addlinespace
\bottomrule
\end{tabularx}
\end{sidewaystable}
The situations for classical quantities, the computational power above
them, and their inspired quantum models are summarized in Table~\ref{tab:Comparison}.
Similar to classical analog computers, the quantum circuit model,
the most widely used model of quantum computing, manipulates quantities
which are not discrete apparently: the probability amplitudes of quantum
states. It is reasonable to expect the similar inconsistency between
classical classical quantities and their mathematical representation
applies to the quantum case as well. To address this issue, we will
start from the ``conventional quantum theory'' reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
and ``ordinary'' quantum theory.}, where the probability amplitudes are in the field of complex numbers.
On one hand, if the probability amplitudes are assumed to be ultimately
discrete, we replace the field of complex numbers by discrete finite
fields and consider the quantum theories and computing over finite
fields. On the other hand, if the probability amplitudes are never
quantized no matter how hard we try, we still should not be able to
access their exactly values. This inaccessibility is essentially the
same as the measurement precision should only be finite, which will
be incorporated into the quantum theory by our quantum interval-valued
probability measures (QIVPM) framework.

\todo{Introduction Cleaned up until here. }Because we are agnostic
about whether probability amplitude is quantized or can really be
valued in the continuum of complex numbers, we tried to develop two
different types of models: the quantum theories and computing over
finite fields are discrete models, and the quantum interval-valued
probability measures incorporate the idea of measurement precision
into the quantum theory. .

\todo{Beginning of Merge Left}Since conventional probability amplitude
is in the field of complex numbers, and the field structure is essential
to compute the probability from some probability amplitudes, we in
Chapter~\ref{chap:DQT=000026DQC} tried to build discrete quantum
theories and computing by considering them over finite fields.

Since error analysis technique cannot always compensate the inevitable
problem of measurement precision, we then incorporate the idea of
finite precision measurement into the quantum theory in Chapter~\ref{chap:QIVPM},
and hope it could describe the physical reality and computability
more faithful.\todo{End of Merge Left}

\todo{Beginning of Merge Right}We begin by replacing the continuum
of complex numbers by discrete finite fields in quantum theory. The
simplest theory, defined over unrestricted finite fields, is so weak
that it only predict whether the measure result is possible or impossible.
Its computational model is also weak that it cannot express Deutsch's
algorithm, but, paradoxically, is also so powerful that it can be
used to solve the $\usat$ problem, which is as hard as a general
$\NP$-complete problem.

@@

Finally, we shift our attention to consider quantum interval-valued
probability measures (IVPMs), which potentially embody both finite
precision measurement and a sensible correspondence to standard quantum
probability. This interval-valued framework not only provides a natural
generalization of both classical IVPMs and conventional quantum probability
measures, but also allows us to establish bounds on the validity of
the Kochen-Specker and Gleason theorems in realistic experimental
environments.\todo{End of Merge Right}

@@

\begin{tabularx}{\linewidth}{YYYYYYY}
\toprule 
\addlinespace
 & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline\addlinespace
\addlinespace
\midrule
\midrule 
\addlinespace
 & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & Local region in $\Fpp^{D}$ & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Likelihood of events is predicted by & Real-valued probability & Possible or impossible & Possible or impossible & Cardinal probability & Real-valued probability, but no sensible Born rule & Interval-valued probability\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Expectation value & Defined & Undefined & Undefined & Undefined &  & Defined\tabularnewline\addlinespace
\addlinespace
\midrule
\midrule 
\addlinespace
 &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Hadamard transformation & Included & May not be included & Included & Included &  & \tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Solve $\usat$ efficiently & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Grover search algorithm & Yes &  &  & Yes &  & \tabularnewline\addlinespace
\addlinespace
\bottomrule
\end{tabularx}
\end{sidewaystable}

@@

\chapter{Quantum Theories and Computing over Unrestricted Finite Fields}

@@

\begin{proof}Assume the function $f$ is satisfiable at some input
$a_{1},a_{2},\ldots,a_{n}$ denoted $\overline{a}$, and where $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$.
In the second step, the state becomes $\ket{0}\ket{\overline{+}}$
as above. We can write this state as $\ket{0}\ket{\overline{a}}+\Sigma_{\overline{x}\neq\overline{a}}\ket{0}\ket{\overline{x}}$.
Applying $U_{f}$ produces $\ket{1}\ket{\overline{a}}+\Sigma_{\overline{x}\neq\overline{a}}\ket{0}\ket{\overline{x}}$.
We can rewrite this state as $\ket{+}\ket{\overline{a}}+\Sigma_{\overline{x}}\ket{0}\ket{\overline{x}}=\ket{+}\ket{\overline{a}}+\ket{0}\ket{\overline{+}}$,
where the summation is now over all vectors (notice that $\ket{0}\ket{\overline{a}}+\ket{0}\ket{\overline{a}}$
is the zero vector). Applying $S$ to each qubit in the second component
produces $\ket{+}\ket{\overline{S(a)}}+\ket{0}\ket{\overline{0}}$.
Applying $S^{\dagger}$ to the first component produces: $\ket{1}\ket{\overline{S(a)}}+\ket{0}\ket{\overline{0}}$.
Applying control-not gate, which applying $\sigma_{0}$ or $\sigma_{x}$
on the second component depending on the first component of the state,
and produces 
\begin{equation}
\ket{1}\left(\sigma_{x}\ket{\overline{S(a)}}\right)+\ket{0}\left(\sigma_{0}\ket{\overline{0}}\right)=\ket{1}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}\,.
\end{equation}
Applying $S^{\dagger}$ to the first component produces $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}$.
For the measurement of $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}$
to be guaranteed to never be $\ket{0}\ket{\overline{0}}$, we need
to verify that $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}$
has one occurrence $\ket{0}\ket{\overline{0}}$. \todo{The following
need to be rewritten. }This can be easily proved as follows. Since
each $a_{i}$ is either 0 or 1, then each $S(a_{i})$ is either $+$
or $1$, and hence each $\mathsf{not}\left(S(a_{i})\right)$ is either~$+$
or~$0$. The result follows since any state with a combination of
$+$ and $0$, when expressed in the standard basis, would consist
of a superposition containing the state $\ket{0\ldots}$.\end{proof}%
\begin{comment}

\section{Modal Quantum Theory and Computing}

Our first discrete model replaces the complex numbers by a unrestricted
finite field~$\mathbb{F}_{q}$ \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
In this model, an $n$-qubit state is a non-zero vector in $\mathbb{F}_{q}^{2^{n}}$.
When we measure a given state~$\ket{\Phi}$, an observable is replaced
by a basis~$\mathcal{B}$ of $\mathbb{F}_{q}^{2^{n}}$. Since $\ket{\Phi}$
can be represented by the summation across a unique subset~$\mathcal{S}$
of the basis~$\mathcal{B}$, whether it is possible or impossible
to measure a basis vector~$\ket{i}$ depends on whether $\ket{i}$
is in $\mathcal{S}$ or not. Because this model only predicts whether
a result is possible or impossible, it is called the modal quantum
theory. Its computational model, called the modal quantum computing,
is far from conventional quantum computing. Although modal quantum
computing can express simple algorithms such as quantum teleportation
\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007}.
This quantum theory is, however, also so powerful that it can be used
to solve an unstructured database search of size $N$ using $O(\log(N))$
steps, which outperforms the known asymptotic bound $O(\sqrt{N})$
in conventional quantum computing \cite{Grover:1996:FQM:237814.237866,BennettBernsteinBrassardVazirani1997,Mermin2007,Jaeger2007}.
\end{comment}

@@

\subsection{Partial \usat\ Algorithm}

>>>>

After first suggested by Richard Feynman 40 years ago~\cite{Feynman1982Simulating},
IBM, \textitalian{Rigetti}, Google, Microsoft, and many other companies
and countries start to build realistic quantum computers recently
\cite{Shieber2018,Kahn2019}, and seek more efficient ways to simulate
chemical molecules and to break down RSA \cite{boneh1999twenty,wiki:RSAFactoring}.
No matter how to, classical or quantum, attack these two tasks, they
require two different types of quantities. On one hand, a question
and its answer of RSA are both discrete integers. On the other hand,
molecules are described by quantities including the domain of their
position wave functions or the probability amplitudes of a wave function.
Even if these quantities look like continuous, we want to argue that
these quantities might later be discovered to be discrete. Even if
they were not discrete, this fact may never be proved and the exact
value of these quantities may never be pinned down. To better understand
this issue without struggling with the quantum theory, it is instructive
to review how classical quantities are characterized and computed.

@@

Although it is convenient to assume physical quantities is as continuous
as their mathematical models, each physical quantity discussed in
the previous paragraph could not have a simple one-to-one correspondence
with a real number. Chuang-tzu's stick are made by molecules and cannot
be cut in halves endlessly. The input charge of an integrator must
actually be an integer multiple of the elementary charge. A prefect
square cannot be draw physically. Even we don't draw it, but merely
ask whether it exists in the space. This question is still beyond
our ability to answer because whether the space itself is ultimately
discrete or continuous is still an unsolved question. Even if a prefect
square exists physically, we may not able to decide whether the ``square''
we discussed is really prefect or almost prefect differing only by
an arbitrarily small extent. Similar situation applying to the length
of a slide rule, it is beyond our ability to decide whether its length
is ultimately discrete or continuous. Even if its length is continuous,
identifying which real number represents its length requires infinite
precision, but the precision in reality is limited generally three
or four significant figures~\cite{wiki:AnalogComputer}. As the results,
even if analog computers really store real numbers, they cannot be
precisely read, written, and used to branch the computation. The opposite
of the last statement is sometimes assumed by real computational models.
For example, Blum, Cucker, Shub, and Smale modeled their BCSS machine
to allow the operations of deciding whether a number is greater or
equal to zero over real numbers and whether a number is exactly zero
over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
Hence, even if the inputs of an analog computer and a BCSS machine
are close to each other, their computational results might be completely
different, like the butterfly effect, and may not be compensated by
error analysis techniques. Therefore, the computational power of analog
computers is far weaker than the prediction based on this kind of
theoretical models.

\begin{sidewaystable}
\caption{\label{tab:Comparison}Comparison between the classical quantities
and their mathematical models with the inspired quantum models. \todo{Center
entries vertically.}}

\centering{}\centering{}%
\begin{tabularx}{\linewidth}{ccYY}
\toprule 
\addlinespace
Physical quantities & Discrete & Discrete with extreme small unit & Continuous?\tabularnewline\addlinespace
\addlinespace
\addlinespace
Computational devices & Digital computer & Analog computer & Analog computer\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Mathematical representation & Integers & Real numbers & Real numbers\tabularnewline\addlinespace
\addlinespace
\addlinespace
Computational model  & Turing machine & BCSS machine & BCSS machine\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
How the models realize? & Reliably & 
Not reliably, but after we have a better technology to manipulate the minimum units, we can predict the physical phenomenon and their computational power by a better discrete model. & 
Not reliably, because precision can never be high enough, and the difference between their computational power might not be compensated by error analysis techniques. \tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Inspired quantum models &  & Quantum Theories and Computing over Finite Fields & Quantum Interval-Valued Probability Measures (QIVPM)\tabularnewline\addlinespace
\addlinespace
\bottomrule
\end{tabularx}
\end{sidewaystable}
The situations for classical quantities and the computational power
above them are summarized in Table~\ref{tab:Comparison}, and the
two possibilities dealing with real-valued models inspires us two
types of quantum models. Similar to classical analog computers, the
quantum circuit model, the most widely used model of quantum computing,
manipulates quantities which are not discrete apparently: the probability
amplitudes of quantum states. To address the similar inconsistency,
we first review the ``conventional quantum theory'' in Chapter~\ref{chap:Conventional-Quantum-Theory}\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
and ``ordinary'' quantum theory.}, where the probability amplitudes are in the field of complex numbers.
If the probability amplitudes are assumed to be ultimately discrete,
we replace the field of complex numbers by discrete finite fields
and consider the quantum theories and computing over finite fields.
Another possibilities could be that the probability amplitudes are
never quantized no matter how hard we try, and we could never access
their exactly values. Notice that the probability amplitudes can never
be accessed directly in an experiment, the accessible properties of
a quantum system is its measurement results and the probability of
an event. Hence, to incorporate the finite precision measurement into
the quantum theory, we consider a framework called quantum interval-valued
probability measures (QIVPM).

\begin{comment}
Our first discrete model replaces the complex numbers by a unrestricted
finite field~$\mathbb{F}_{q}$ \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
In this model, an $n$-qubit state is a non-zero vector in $\mathbb{F}_{q}^{2^{n}}$.
When we measure a given state~$\ket{\Phi}$, an observable is replaced
by a basis~$\mathcal{B}$ of $\mathbb{F}_{q}^{2^{n}}$. Since $\ket{\Phi}$
can be represented by the summation across a unique subset~$\mathcal{S}$
of the basis~$\mathcal{B}$, whether it is possible or impossible
to measure a basis vector~$\ket{i}$ depends on whether $\ket{i}$
is in $\mathcal{S}$ or not. Because this model only predicts whether
a result is possible or impossible, it is called the modal quantum
theory. Its computational model, called the modal quantum computing,
is far from conventional quantum computing. Although modal quantum
computing can express simple algorithms such as quantum teleportation
\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007}.
This quantum theory is, however, also so powerful that it can be used
to solve an unstructured database search of size $N$ using $O(\log(N))$
steps, which outperforms the known asymptotic bound $O(\sqrt{N})$
in conventional quantum computing \cite{Grover:1996:FQM:237814.237866,BennettBernsteinBrassardVazirani1997,Mermin2007,Jaeger2007}.
\end{comment}
When replacing the continuum of complex numbers by discrete finite
fields, we first doesn't restrict our quantum theory and computing
over which finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
\cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
This theory is called modal quantum theory because it is so weak that
it only predict whether the measure result is possible or impossible,
and even the expectation value of an observable is not able to be
defined. Although a version of quantum theory defined over a two-valued
field can express simple algorithms such as quantum teleportation
\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007}.
This quantum theory is, however, also so powerful that it can be used
to solve the $\usat$ problem, which is as hard as a general $\NP$-complete
problem.

\todo{Introduction Cleaned up until here. }Next, in Sec.~\ref{discretequantumtheoryI}
to \ref{sec:Geometry-of-Entangled-States}, we improve on this by
showing that for finite fields of order $p^{2}$, with the prime $p$
of the form $4\ell+3$ ($\ell$ a non-negative integer), the complex
numbers have extremely compelling and natural discrete analogs that
permit a great many of the standard requirements of quantum computing
to be preserved. Under suitable conditions, we have amplitude-based
partitions of unity, unitary transformations, and entanglement, as
well as solutions to deterministic quantum algorithms such as the
algorithms of Deutsch, Simon, and Bernstein-Vazirani, though still
with some bothersome shortcomings. Because of the modular nature of
arithmetic in the finite complex field, it is not possible to define
an inner product in the usual sense, and we show in Sec.~\ref{subsec:Partial-Algorithm}
that this leads to excessive computational power for the unstructured
database search problem for certain database sizes.

@@

Finally, we shift our attention to consider quantum interval-valued
probability measures (IVPMs), which potentially embody both finite
precision measurement and a sensible correspondence to standard quantum
probability. This interval-valued framework not only provides a natural
generalization of both classical IVPMs and conventional quantum probability
measures, but also allows us to establish bounds on the validity of
the Kochen-Specker and Gleason theorems in realistic experimental
environments.

@@

\begin{tabularx}{\linewidth}{YYYYYYY}
\toprule 
\addlinespace
 & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline\addlinespace
\addlinespace
\midrule
\midrule 
\addlinespace
 & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & Local region in $\Fpp^{D}$ & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Likelihood of events is predicted by & Real-valued probability & Possible or impossible & Possible or impossible & Cardinal probability & Real-valued probability, but no sensible Born rule & Interval-valued probability\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Expectation value & Defined & Undefined & Undefined & Undefined &  & Defined\tabularnewline\addlinespace
\addlinespace
\midrule
\midrule 
\addlinespace
 &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Deutsch's algorithm & Yes & Maybe no & Yes & Yes &  & \tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Solve $\usat$ efficiently & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Grover search algorithm & Yes &  &  & Yes &  & \tabularnewline\addlinespace
\addlinespace
\bottomrule
\end{tabularx}
\end{sidewaystable}

@@

\chapter{Quantum Theories and Computing over Unrestricted Finite Fields\label{chap:Unrestricted-Finite-Fields}}

@@

\begin{proof}Assume the function $f$ is satisfiable at some input
$a_{1},a_{2},\ldots,a_{n}$ denoted $\overline{a}$, and where $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$.
In the second step, the state becomes $\ket{0}\ket{\overline{+}}$
as above. We can write this state as $\ket{0}\ket{\overline{a}}+\Sigma_{\overline{x}\neq\overline{a}}\ket{0}\ket{\overline{x}}$.
Applying $U_{f}$ produces $\ket{1}\ket{\overline{a}}+\Sigma_{\overline{x}\neq\overline{a}}\ket{0}\ket{\overline{x}}$.
We can rewrite this state as $\ket{+}\ket{\overline{a}}+\Sigma_{\overline{x}}\ket{0}\ket{\overline{x}}=\ket{+}\ket{\overline{a}}+\ket{0}\ket{\overline{+}}$,
where the summation is now over all vectors (notice that $\ket{0}\ket{\overline{a}}+\ket{0}\ket{\overline{a}}$
is the zero vector). Applying $S$ to each qubit in the second component
produces $\ket{+}\ket{\overline{S(a)}}+\ket{0}\ket{\overline{0}}$.
Applying $S^{\dagger}$ to the first component produces: $\ket{1}\ket{\overline{S(a)}}+\ket{0}\ket{\overline{0}}$.
Applying control-not gate, which applying $\sigma_{0}$ or $\sigma_{x}$
on the second component depending on the first component of the state,
and produces 
\begin{equation}
\ket{1}\left(\sigma_{x}\ket{\overline{S(a)}}\right)+\ket{0}\left(\sigma_{0}\ket{\overline{0}}\right)=\ket{1}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}\,.
\end{equation}
Applying $S^{\dagger}$ to the first component produces $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}$.
For the measurement of $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}$
to be guaranteed to never be $\ket{0}\ket{\overline{0}}$, we need
to verify that $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}$
has one occurrence $\ket{0}\ket{\overline{0}}$. \todo{The following
need to be rewritten. }This can be easily proved as follows. Since
each $a_{i}$ is either 0 or 1, then each $S(a_{i})$ is either $+$
or $1$, and hence each $\mathsf{not}\left(S(a_{i})\right)$ is either~$+$
or~$0$. The result follows since any state with a combination of
$+$ and $0$, when expressed in the standard basis, would consist
of a superposition containing the state $\ket{0\ldots}$.\end{proof}

@@

\subsection{Partial \usat\ Algorithm\label{subsec:Partial-Algorithm}}
